---
title: "Base R- Weekly Assignment #2"
author: "Amanda Mae Woodward"
date: "2022-10-03"
output: html_document
---
# Set Up
1. Load the tidyverse library. 
```{r}
library(tidyverse)
library("ggplot2")
```
#√- you don't need to load ggplot 2. on my end, using library("ggplot2") does not work. I had to remove the quotation marks
2. Load the billboard data. 
```{r}
data("billboard")
```
#√
3. What type of data is this? (e.g. describe what's in the dataset.)
```{r}
#This data looks like ordered factor data because the numbers for each song and artist are the rank they took within the top 100 for each week.
```
#√ - i just meant what the data are (in this case songs from the billboard top 100 in 2000) 
4. Print the column names from this dataset. 
```{r}
print(colnames(billboard))
```
#√- print is redundant, but ok to include
5. Print the first 5 entries in the dataset. 
```{r}
print(head(billboard, 5))
```
#√

# Practice
1. Create a subset of data that has Jay-Z as the only artist. How many songs are in it?
```{r}
JayZStats<- billboard %>%
  filter(artist=="Jay-Z")
```
#√ How many songs? 
2. In the original dataset, use filter to find information about the song "All the small things." What was the highest position this song reached on the billboard 100? 
```{r}
ATST<- billboard %>%
  filter(track=="All The Small Things")
#6
```
#√
3. Create a subset of data for songs Tim McGraw sang. Summarize the data for wk 1.
```{r}
TimMcGrawSongs<- billboard %>%
  filter(artist=="McGraw, Tim")
summary(TimMcGrawSongs$wk1)
```
#√
